{\fontsize{16pt}{19.2pt}\selectfont\bf{\begin{center}
ABSTRACT
\end{center}}}

\vspace*{1cm}

In today’s world, there is a constant quest to minimize the work of humans, save labor, conserve energy, and improve the accuracy, quality, and precision of any work. This leads to automation. Automation or automatic control is the use of various control systems for operating equipment or for completing a task with minimal or reduced human intervention. Some processes are completely automated while others are partially automated, depending on the task. Several industries have already automated their manufacturing units and assembly units, drastically reducing costs and increasing their outputs. An industry that can benefit from such automation is the Retail/ Supermarket industry.


Lots of people use supermarkets. These supermarkets can get crowded during festivals, special occasions or even during rush hours every day. While it is great for the supermarket to have so many people willing to buy at their store, increasing its revenue, the long lines at billing counters can be a great deterrent for potential customers. Long lines have a tendency to drastically reduce perceived customer satisfaction. It could even mean some potential customers may decide to give up and leave the store without buying anything. In fact, lines that are "too long" are the second most common complaint of consumers against retailers (the first complaint being that the members of the staff are "rude"). Surveys have revealed that the customers don’t like waiting in queues because they feel that they are wasting their time and being unproductive. When they finally get their turn at the billing counter, they often meet a rude and harassed employee. This further serves to take away from the overall good impression of the store the customer might have otherwise formed.


While the above problem can be dealt with temporarily by distracting the consumers with strategically placed merchandise or explaining the reason for the delays caused, the root of the problem – long lines doesn’t go away. A feasible solution that might permanently address the problem of long lines is the automation of the billing process.